Output Summary

### 2020-09-24 03-post-process/output-plots.Rmd
Add MCMC diagnostic plots

>>>>

## Diagnostic Plots {.tabset .tabset-pills}

### `alpha`, `beta`

```{r alpha-beta-diag-plots, fig.width = 4, fig.height = 5}
diag_plots(post, c("alpha", "beta"), layout = "2x1")
```

### `^mu`

```{r mu-diag-plots, fig.width = 7, fig.height = 7}
diag_plots(post, "^mu", layout = "5x3")
```

### `^sig`

```{r sig-diag-plots, fig.width = 7, fig.height = 7}
diag_plots(post, "^sig", layout = "5x3")
```

### `init_recruits`

```{r init-recruits-diag-plots, fig.width = 5, fig.height = 7}
diag_plots(post, "init_recruits", layout = "4x2")
```
